\LARGE \bf Budgeted Multi-Armed Bandit Models for Sample-Based Grasp Planning in the Presence of Uncertainty [v2]

### 2014-12-31 paper.tex
changed teasr phot and sensitivity analysis, also wrote over stuff

\title{\LARGE \bf
Budgeted Multi-Armed Bandit Models for Sample-Based Grasp Planning in the Presence of Uncertainty}

@@

\begin{abstract}
\textit{Abstract---}Sampling perturbations in shape, state, and control can facilitate grasp planning in the presence of uncertainty arising from noise, occlusions, and surface properties such as transparency and specularities.  Monte-Carlo sampling is computationally demanding, even for planar models. We consider an alternative based on the multi-armed bandit (MAB) model for making sequential decisions, which can apply to a variety of uncertainty models.  We formulate grasp planning as a ``budgeted multi-armed bandit model" (BMAB) with finite stopping time to minimize ``simple regret", the difference between the expected quality of the best grasp and the expected quality of the grasp evaluated at the stopping time.  To evaluate MAB-based sampling, we compare it with Monte-Carlo sampling for grasping an uncertain planar object with shape uncertainty defined by a Gaussian process implicit surface (GPIS), but the method is also applicable to other models of uncertainty.  We derive distributions on contact points, surface normal, and center of mass under shape uncertainty and use these to formulate the associated MAB model, finding that it computes grasps of similar quality to Monte-Carlo sampling and can reduce computation time by an order of magnitude.  This suggests a number of new research questions about how MAB can be applied to other models of uncertainty and how different MAB solution techniques can be applied to further reduce computation.
\end{abstract}

@@

@@

\begin{figure}[t!]
\centering
\includegraphics[width=8.5cm,height=8cm]{figures/Slide02.jpg}
\caption{\footnotesize
Convergance in regret of the bandit sampling method (red), compared to the traditional Monte-Carlo method. The fast convergence of the bandit method is due to its ability to intelligently pick what grasp to sample next in a given set of proposed grasps on an object with shape uncertainty}
\vspace*{-10pt}
\label{fig:noisy data}
\end{figure}

@@

Past work on grasping under uncertainty has considered state uncertainty \cite{goldberg1990bayesian, stulp2011learning}, uncertainty in contact locations with an object \cite{zheng2005}, uncertainty in object pose \cite{christopoulos2007handling, weisz2012pose, kim2012physically}.
The effect of uncertainty in object geometry on grasp selection has been studied for spline representations of objects~\cite{christopoulos2007handling}, extruded polygonal mesh models~\cite{kehoe2012estimating, kehoe2012toward}, and point clouds~\cite{hsiao2011bayesian}.

Currently, the most common method of evaluating the expected grasp quality under uncertainty is to rank a set of random grasps on an object using  samples on shapes, pose or parameters to evaluate a quality measure~\cite{christopoulos2007handling, kehoe2012estimating, kehoe2012toward}.
Monte-Carlo sampling involves drawing random samples from a distribution to approximate an expected value\cite{caflisch1998monte}, which can be slow when the distribution is high-dimensional, such as for distributions on possible shapes.
To address this, Kehoe et al.~\cite{kehoe2012estimating} demonstrated a procedure for finding a minimum bound on expected grasp quality given shape uncertainty, which reduced the number of terms needed in Monte-Carlo sampling in order to choose the highest quality grasps. The adaptive sampling pruned grasps using only the sample mean and did not utilize any estimates of how accurate the current sample mean is. 
Laaksonen et al.~\cite{laaksonen2012probabilistic} used Markov Chain Monte-Carlo (MCMC) sampling to estimate grasp quality and object pose  under shape and pose uncertainty.
MCMC simplified sampling from a complicated joint distribution on pose and shape, but it can be slow to converge to the correct distribution due to burn in and mixing conditions~\cite{andrieu2003introduction}.

We chose to study our MAB sampling method for shape uncertainty using a Gaussian process implicit surface representation. Our decision to use this uncertainty model is based on GPIS's ability to combine various modes of noise observations such as tactile, laser and visual~\cite{rasmussen2006, williams2007, dragiev2011} and its recent use in modeling uncertainty for a number of robotic applications.
Hollinger et al. used GPIS as a model of uncertainty and performed active sensing on the hulls in underwater boats \cite{hollinger2013}.
Dragiev et al. showed how GPIS can enable a grasp controller on the continuous signed distance function \cite{dragiev2011}.
Mahler et al. used the GPIS representation to find locally optimal anti-podal grasps by framing grasp planning as an optimization problem \cite{mahler2015opt}. However, this relied on an approximation to grasp quality without guarantees on accuracy.. We propose an adaptive sampling approach known as the Multi-Armed Bandit Model.

\section{Preliminaries and Problem Definition}
Before we present the problem definition, we introduce a way to evaluate the quality of a grasp and our grasping model, the line of action.

@@

The $L^1$ version of the metric depends on the contact points $\textbf{c}_1,...,\textbf{c}_m \in \mathcal{R}^2$, surface normals $\textbf{n}_1,...,\textbf{n}_m \in \mathcal{R}^2$, center of mass $\textbf{z}$ and friction coefficient $\mu$. Then the metric is evaluated by constructing a convex hull around the wrenches made up of those parameters and finding the radius of the largest unit ball centered at the origin in wrench space. If the convex hull does encloses the origin then the grasp is in ``force-closure,'' meaning the grasp can resist any external wrenches if enough force is used. Thus if the hull does not enclose the origin then there exists a wrench that the grasp is not able to resist, which occurs if the quality metric $Q$ is less than zero. Thus a grasp can be parameterized by the following tuple $g = ( \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} )$.

In this work we use the probability of achieving force closure, or $P(Q>0)$, \cite{christopoulos2007handling}\cite{kehoe2012toward}, to rank grasps . $P(Q>0)$ may be computed by sampling from our distributions on pose, shape and material properties (friction coefficient and center of mass) and averaging the qualities that are computed. Reducing the time to find the grasp with the highest probability of force closure from a set of a large number of grasps is the primary focus of the paper.

@@

\subsection{Types of Uncertainty}
In this work we consider the following types of uncertainty shape, pose, movement, and friction coefficient.  The property of force closure is not effected by the center of mass because it only measures if a wrench can be resisted not how large the force is need to resist.  Fig. \ref{fig:graphical_model} shows the probabilistic relationship of all types of uncertainty considered in this work. We model each one of these with a corresponding distribution and demonstrate how MAB algorithms can handle all types of uncertainty.

@@

Shape uncertainty can occur from transparency, occlusions and sensor noise \cite{mahler}. To model this uncertainty we chose to use a Gaussian Process Implicit Surface (GPIS) representation, which is explained in detail in Sec. \ref{sec:Appendix}.  A GPIS is a Gaussian distribution on a signed distance function,$sd$, that describes the workspace. A signed distance function is  greater than 0 outside the surface of an object, 0 at the surface and less than 0 beneath.  The GPIS can be sampled from via $N(\mu(x),\Sigma(x))$, where $\mu(x)$ and $\Sigma(x)$ are the mean and covariance functions of the GPIS. For our application, we set $x$ to discretized points along the workspace $\mathcal{W}$ and for each sample the points that correspond to zero, $sd(x) = 0$, are the contours of the shape. We will henceforth  represent the $\mu(x)$ and $\Sigma(x)$ as the tuple $\theta = \left( \mu(x), \Sigma(x) \right)$.

@@

\todo{Jeff: Put equations here. Sorry my internet is too slow to download the paper i need right now}

 \subsubsection{Distribution on Motion}
 In practice a robot may not be able to execute a desired
grasp plan $\Gamma$ exactly due to errors in trajectory following or
registration to the object \cite{kehoe2012estimating}. To handle this uncertainity, we sample the angle of approach $\rho$ of the proposed grasp plan $\Gamma$ from a zero mean one-dimensional Guassian $\rho \sim N(0,\sigma^2)$. In practice $\sigma^2$ might be set from repeatibility measurements for a robot \cite{mooring1986determination}.

@@

To evaluate the $P(Q(\Gamma)>0)$, we sample from the graphical model shown in Fig. \ref{fig:graphical_model}. In the naive way sampling from the graphical model could be slow, however our goal is not to actually determine the probability of force closure but instead to determine the best grasp in a set $G$. Thus, our BMAB algorithms can efficiently sample from theses priors on the different types of uncertainty.

\begin{figure}[ht!]
\centering
\includegraphics[width = 6cm, height = 6cm]{figures/Slide8.jpg}
\caption{A graphical model that illustrates the relationship between the different types of uncertainty in an object. Center of Mass uncertainty is dependent on the pose and shape of the object, however friction coefficient is independent of all other types. }
\vspace*{-10pt}
\label{fig:graphical_model}
\end{figure}

@@

\section{Multi-Armed Bandits for Grasp Selection}
While a standard approach to solving the problem in Eq. \ref{eq:problem_def} would be to perform Monte-Carlo integration on each $\Gamma_i$ and compute the probability of force closure, we propose treating the problem as a multi-armed bandit model and forming a policy for selecting which grasp to sample. 
In our setting, we have a probabilistic shape representation and would like to evaluate many potential grasps on that shape model.
Motivated by limited computational resources we are interested in how to intelligently allocate sampling resources to efficiently find the best grasp plan $\Gamma^*$.
Here each arm corresponds to a different grasp plan and pulling the arm is sampling from the graphical model in Fig. \ref{fig:graphical_model} and evaluating the arm's grasp plan on the sample.
The reward for pulling an arm is 1 if the grasp is in force closure on the sample and 0 if the grasp is not in force closure.

We can now model the distribution on rewards as a Beta-Bernoulli process. Bernoulli distributions are formally the probability $\theta$ that an event has occurred and a Beta distribution is the conjugate prior on the probability of theta or $p(\theta)$. Beta distributions are specified by shape parameters $\alpha$ and $\beta$, to update the prior Beta distribution one simply adds the count of observed successes of the event to $\alpha$ and the count of the observed failures to $\beta$. The default $\alpha =1 $ and $\beta =1$ corresponds to a uniform distribution on $\theta$.

Where $Q(\Gamma|\theta,\xi,\mu,z)$ is the grasp quality that is computed on a shape sample drawn from $p(\theta)$,$p(\xi)$,$p(\rho)$ and $p(\mu)$. To compute this we intersect the zero crossing of the level set with the propose grasp plan $\Gamma$ and determine the parameters $g$, this has been the approach taken in previous work  \cite{kehoe2012estimating}, \cite{kehoe2012toward},  \cite{christopoulos2007handling}. Whats interesting in the context of a BMAB problem our complicated graphical model in Fig. \ref{fig:graphical_model}, is now equivalent in terms of inference to \ref{fig:beta_model} and we only need to estimate $\alpha$ and $\beta$ to determine grasp quality. It is this intuition that helps explain the performance of the BMAB algorithm.

\section{Multi-Armed Bandit Model}
The multi-armed bandit model, originally described by Robbins \cite{robbins1985some}, is a statistical model of an agent attempting to make a sequence of correct decisions while concurrently gathering information about each possible decision.
The traditional setting of a multi-armed bandit model is a gambler that has K independent slot machine arms and decides what machines to play, how many times to play each one, what order to play them in.
A successful gambler would want to exploit the machine that currently yields the highest reward and explore new arms to see if they give better rewards.
Developing a policy that successfully trades between exploration and exploitation has been the focus of extensive research since the problem formulation \cite{bubeck2009pure}, \cite{robbins1985some}, \cite{bergemann2006bandit}.
%Solutions to the multi-armed bandit model have been used in applications for which evaluating all possible options is expensive or impossible, such as the optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.

A common measure of success in MAB problems is {\it regret}, the difference between the expected optimal reward and the expected reward of the selected arm on a single pull.
Traditional bandit algorithms minimize cumulative regret,  the sum of regret over the entire sequence of arm choices. There are a number of algorithms for developing policies to balance exploration and exploitation.
One algorithm is $\epsilon-$greedy, which is the idea of choosing the arm with the highest empirical expected reward with $1-\epsilon$ probability and choosing a random arm with probability $\epsilon$ \cite{barto1998reinforcement}.
A class of algorithms that have stronger theoretical guarantees are from the Upper Confidence Bound (UCB) family.
For each arm, UCB algorithms maintain the empirical expected reward and an upper confidence bound on the true expected reward using concentration inequalities for the assumed reward distribution.

%In our case we only care about the regret at the time our decision of the optimal grasp needs to be made, decoupling the exploration and exploitation stages.
In our case we only care about regret at the time our decision of the optimal grasp has been made, decoupling the exploration and exploitation stages. 
%For example in medical testing for patients it is important to always administer the best treatment for the given patient. %However for the case of product testing in cosmetics it does not matter what products are administer in the testing phase, but only what final product is sold to the consumer.
Thus our goal is to identify the best arm in as few decisions as possible.
Given a set of arms $\lbrace 1,...K \rbrace$ with respective mean rewards $\mu_1, ..., \mu_K$ and the optimal arm $\mu^* = \underset{k\in\lbrace 1, ..., K \rbrace}{\mbox{max}} \mu_k$.
The simple regret at time $t$ is given by

@@

\label{sec:bandit_algorithm}
\section{Bandit Algorithms For Best Arm Identification}\label{sec:algorithms}
\subsection{Thompson Sampling}
Thompson Sampling is a Bayesian method for the multi-armed bandit problem. The main idea behind it is to update the conjugate prior for the distribution of the arm recently pulled, then sample from the prior distribution on all arms and pull the arm with the highest sample drawn. The full algorithm is shown in Algorithm 1.  Empirically this method has been shown to outperform frequentist methods like UCB in certain settings \cite{chapelle2011empirical}

@@

\subsection{Upper Confidence Bound (UCB)}
The UCB strategy was the first strategy shown to have asymptotic logarithmic regret \cite{lai1985asymptotically} for distributions with bounded rewards. UCB estimates an empirical confidence bound for each arm based on the observations seen so far., then pulls the arm with the highest confidence bound. The confidence interval is derived from various concentration inequalities. The algorithm is in Algorithm 2 and assumes a Beta-Bernoulli Distribution, which matches our assumption of a 0-1 success measure for grasping.

\begin{algorithm}
 \KwResult{Best Arm, $g^*$ }
\For{ t=1,2,...}{ 
 Pick arm: $ k = \underset{k\in{1,...,K}}{\mbox{argmax}} \mu_k + \sqrt{\frac{6\mbox{log}(t)}{T_k}}$\\
 Observe reward $X_{k_t,t} \in \lbrace 0,1 \rbrace$\\
 Update\\
 $T_k= T_k +1$\\
 $\mu_k = \frac{T_k-1}{T_k}*\mu_k + \frac{1}{T_k}*X_{k,t}$\\
 }
 \caption{UCB for Beta-Bernoulli Process}
\end{algorithm}

\subsection{The Gittins Index Method} 
One possible solution to solve the MAB problem is to treat it as an Markov Decision Process (MDP) and use Markov Decision theory. This solution makes a lot of sense when the distribution is known because the all elements in the standard MDP tuple, $\lbrace S,A,T,R,\gamma \rbrace$, would be known and it is optimal with respect $\gamma$.

@@

\section{Distributions on Grasp Parameters}
\label{sec:distgrasp}

 To sample from $p(Q(\Gamma)>0)$, we need to sample from the distributions associated with a line of action $p(\textbf{n}_i,\textbf{c}_i|\gamma_i(t),\xi,\theta, \rho)$. Using Bayes rule and our graphical model we can rewrite this as

 In section \ref{sec:Appendix}, we look at how to draw shape sample from a GPIS model, which is used to compute $p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\xi)$ along with the other sampled distribution on pose ($\xi$) and motion ($\rho$). Then in section \ref{sec:normals}, we look at how to sample from $p(\textbf{n}_i|\textbf{c}_i,\theta)$ and present a novel visualization technique for the distribution on surface normals. Lastly in section \ref{sec:mass}, we show a way to calculate the expected center of mass assuming a uniform mass distribution. 
 .
\subsection{Distribution on Surface Normals}\label{sec:normals} 
Using Eq. \ref{eq:mean_gradient} and Eq. \ref{eq:cov_gradient}, we can compute the mean of the gradient $ \mu_{\nabla}(x)$ and the covariance of the gradient $\Sigma_{\nabla}(x)$ respectively. Thus we can compute the distribution around the surface normal for a given point in $\mathcal{W}$. We can now write

\subsection{Multi-Armed Bandit Experiments}
We consider the problem of selecting the best grasp plan, $\Gamma^*$ out of a set $G$. For our experiments we look at selecting the best grasp out of a size of $|G| = 1000$. In Fig. \ref{fig:simple_regret}, we plotted the simple regret averaged over 100 of the shapes in our data set and compare the different methods (UCB, Thompson, Gittins and the naive random allocation). We initialize both the Monte-Carlo and bandit technique by sampling each grasp 1 time. We draw samples from our calculated distributions $p(g)$.  Interestingly, Gittins and Thompson converge much faster than random and UCB. In Fig. \ref{fig:pulls_per_grasp}, you can see that Gittins and Thompson allocate grasp samples to only the grasps of high quality, thus it is quickly able to ignore the low quality grasps. UCB takes a more conservative approach to sample allocation, which leads to poor performance in the best arm identification problem \cite{bubeck2009pure}.

>>>>

\title{\LARGE \bf
Budgeted Multi-Armed Bandit Models for Sample-Based Grasp Planning in the Presence of Uncertainty [v2] }

@@

\begin{abstract}
\textit{Abstract---}\todo{Not sure if we need to change the authors list or not}Sampling perturbations in shape, state, and control can facilitate grasp planning in the presence of uncertainty arising from noise, occlusions, and surface properties such as transparency and specularities.  Monte-Carlo sampling is computationally demanding, even for planar models. We consider an alternative based on the multi-armed bandit (MAB) model for making sequential decisions, which can apply to a variety of uncertainty models.  We formulate grasp planning as a ``budgeted multi-armed bandit model" (BMAB) with finite stopping time to minimize ``simple regret", the difference between the expected quality of the best grasp and the expected quality of the grasp evaluated at the stopping time.  To evaluate MAB-based sampling, we compare it with Monte-Carlo sampling for grasping an uncertain planar object with shape uncertainty defined by a Gaussian process implicit surface (GPIS), but the method is also applicable to other models of uncertainty.  We derive distributions on contact points, surface normal, and center of mass under shape uncertainty and use these to formulate the associated MAB model, finding that it computes grasps of similar quality to Monte-Carlo sampling and can reduce computation time by an order of magnitude.  This suggests a number of new research questions about how MAB can be applied to other models of uncertainty and how different MAB solution techniques can be applied to further reduce computation.
\end{abstract}

@@

\begin{figure}%
    \centering
     \subfloat{{\includegraphics[width=8cm]{figures/cup.jpg} }}%

       \qquad

     \subfloat{{\includegraphics[width=8cm]{matlab_figures/teaser.eps} }}%

    \caption{\todo{New teaser photo, not sure if we should have some sort of real object or not}(Top Left) Image of a common household measuring cup. (Top Right) Image from a PR2 Primesense camera that reflects the uncertainty that can be induced in objects from transparency. (Bottom) Comparision of Multi-Armed Bandit Techniques (Bayes UCB, Thompson, Gittins) vs. Monte-Carlo sampling to determine the best grasp in a set of 1000 grasps. As you can see the bandit techniques converge in simple regret Eq. \ref{eq:simple_regret} a magnitude faster than the traditional approach of Monte-Carlo sampling to determine the highest quality grasp.  }%
    \label{fig:rot_shapes}%
\end{figure}

@@

@@

Past work on grasping under uncertainty has considered shape uncertainty \cite{goldberg1990bayesian, stulp2011learning}, uncertainty in contact locations with an object \cite{zheng2005}, uncertainty in object pose \cite{christopoulos2007handling, weisz2012pose, kim2012physically}.
The effect of uncertainty in object geometry on grasp selection has been studied for spline representations of objects~\cite{christopoulos2007handling}, extruded polygonal mesh models~\cite{kehoe2012estimating, kehoe2012toward}, and point clouds~\cite{hsiao2011bayesian}.

Currently, the most common method of evaluating the expected grasp quality under uncertainty is to rank a set of random grasps on an object using  samples on shapes, pose or parameters to evaluate a quality measure~\cite{christopoulos2007handling, kehoe2012estimating, kehoe2012toward}.
Monte-Carlo sampling involves drawing random samples from a distribution to approximate an expected value\cite{caflisch1998monte}, which can be slow when the distribution is high-dimensional, such as for distributions on possible shapes.

To address this, Kehoe et al.~\cite{kehoe2012estimating} demonstrated a procedure for finding a minimum bound on expected grasp quality given shape uncertainty, which reduced the number of terms needed in Monte-Carlo sampling in order to choose the highest quality grasps. The adaptive sampling pruned grasps using only the sample mean and did not utilize any estimates of how accurate the current sample mean is, which in practice could lead to good grasps being thrown away. 
Laaksonen et al.~\cite{laaksonen2012probabilistic} used Markov Chain Monte-Carlo (MCMC) sampling to estimate grasp quality and object pose  under shape and pose uncertainty.
MCMC simplified sampling from a complicated joint distribution on pose and shape, but it can be slow to converge to the correct distribution due to burn in and mixing conditions~\cite{andrieu2003introduction}.

We chose to study our MAB sampling method on distributions for friction coefficient, pose, motion and shape. For shape uncertainty we decided to use a Gaussian process implicit surface representation. Our decision to use this uncertainty model is based on GPIS's ability to combine various modes of noise observations such as tactile, laser and visual~\cite{rasmussen2006, williams2007, dragiev2011} and its recent use in modeling uncertainty for a number of robotic applications.
Hollinger et al. used GPIS as a model of uncertainty and performed active sensing on the hulls in underwater boats \cite{hollinger2013}.
Dragiev et al. showed how GPIS can enable a grasp controller on the continuous signed distance function \cite{dragiev2011}.
Mahler et al. used the GPIS representation to find locally optimal anti-podal grasps by framing grasp planning as an optimization problem \cite{mahler2015gp}. However, this relied on an approximation to grasp quality without guarantees on accuracy.. We propose an adaptive sampling approach known as the Multi-Armed Bandit Model.

\section{Preliminaries and Problem Definition}
Before we present the problem definition, we introduce a way to evaluate the quality of a grasp and our grasping model, the line of action. We also introduce a graphical model to represent the distributions on friction coefficient, motion, pose and shape.

@@

The $L^1$ version of the metric depends on the contact points $\textbf{c}_1,...,\textbf{c}_m \in \mathcal{R}^2$, surface normals $\textbf{n}_1,...,\textbf{n}_m \in \mathcal{R}^2$, center of mass $\textbf{z}$ and friction coefficient $\mu$. Then the metric is evaluated by constructing a convex hull around the wrenches made up of those parameters and finding the radius of the largest unit ball centered at the origin in wrench space. If the convex hull does enclose the origin then the grasp is in ``force-closure,'' meaning the grasp can resist any external wrenches if enough force is used. Thus if the hull does not enclose the origin then there exists a wrench that the grasp is not able to resist, which occurs if the quality metric $Q$ is less than zero. A grasp can be parameterized by the following tuple $g = ( \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} )$\cite{pokorny2013classical}.

In this work we use the probability of achieving force closure, or $P(Q>0)$, \cite{christopoulos2007handling}\cite{kehoe2012toward}, to rank grasps . $P(Q>0)$ may be computed by sampling from our distributions on pose, shape and material properties (friction coefficient) and averaging the qualities that are computed. Reducing the time to find the grasp with the highest probability of force closure from a set of a large number of grasps is the primary focus of the paper.

@@

\subsection{Types of Uncertainty}
In this work we consider the following types of uncertainty shape, pose, movement, and friction coefficient.  The property of force closure is not effected by the center of mass because it only measures if a wrench can be resisted not how large the force is need to resist.  Fig. \ref{fig:graphical_model} shows the probabilistic relationship of all types of uncertainty considered in this work. We model each one of these with a corresponding distribution and demonstrate how MAB algorithms can handle all types of uncertainty. We note though that our choice of distributions does not effect the performance of the MAB algorithm and the reader should choose distribution that effect their needs.

@@

Shape uncertainty can occur from transparency, occlusions and sensor noise \cite{mahler}. To model this uncertainty we chose to use a Gaussian Process Implicit Surface (GPIS) representation, which is explained in detail in Appendix \ref{sec:Appendix}.  A GPIS is a Gaussian distribution on a signed distance function,$sd$, that describes the workspace. A signed distance function is  greater than 0 outside the surface of an object, 0 at the surface and less than 0 beneath.  The GPIS can be sampled from via $N(\mu(x),\Sigma(x))$, where $\mu(x)$ and $\Sigma(x)$ are the mean and covariance functions of the GPIS. For our application, we set $x$ to discretized points along the workspace $\mathcal{W}$ and for each sample the points that correspond to zero, $sd(x) = 0$, are the contours of the shape. For convenience we will  represent the $\mu(x)$ and $\Sigma(x)$ as the tuple $\theta = \left( \mu(x), \Sigma(x) \right)$.

@@

 \subsubsection{Distribution on Motion}
 In practice a robot may not be able to execute a desired
grasp plan $\Gamma$ exactly due to errors in trajectory following or
registration to the object \cite{kehoe2012estimating}. To handle this uncertainity, we sample the angle of approach $\rho$ of the proposed grasp plan $\Gamma$ from a zero mean one-dimensional Guassian $\rho \sim N(0,\sigma_{mot}^2)$. In practice $\sigma_{mot}^2$ might be set from repeatibility measurements for a robot \cite{mooring1986determination}.

@@

To evaluate the $P(Q(\Gamma)>0)$, we sample from the graphical model shown in Fig. \ref{fig:graphical_model}. To sample from $p(Q(\Gamma)>0)$, we need to sample from the distributions associated with a line of action $p(\textbf{n}_i,\textbf{c}_i|\gamma_i(t),\xi,\theta, \rho)$. Using Bayes rule and our graphical model we can rewrite this as

 In Appendix \ref{sec:Appendix}, we look at how to draw shape sample from a GPIS model, which is used to compute $p(\textbf{c}_i|\gamma_i(t),\theta,\rho,\xi)$ along with the other sampled distribution on pose ($\xi$) and motion ($\rho$). Then in Appendix \ref{sec:normals}, we look at how to sample from $p(\textbf{n}_i|\textbf{c}_i,\theta)$ and present a novel visualization technique for the distribution on surface normals. Lastly in Appendix \ref{sec:mass}, we show a way to calculate the expected center of mass assuming a uniform mass distribution.

\begin{figure}[ht!]
\centering
\includegraphics[width = 6cm, height = 6cm]{figures/Slide8.jpg}
\caption{A graphical model that illustrates the relationship between the different types of uncertainty in an object. Center of Mass uncertainty is dependent on the pose and shape of the object, however friction coefficient is independent of all other types. \todo{Should we use words or symbols for the graphical model?}}
\vspace*{-10pt}
\label{fig:graphical_model}
\end{figure}

@@

\section{Multi-Armed Bandits for Grasp Selection}
While a standard approach to solving the problem in Eq. \ref{eq:problem_def} would be to perform Monte-Carlo integration on each $\Gamma_i$ and compute the probability of force closure, we propose treating the problem as a multi-armed bandit model and forming a policy for selecting which grasp to sample. The multi-armed bandit model, originally described by Robbins \cite{robbins1985some}, is a statistical model of an agent attempting to make a sequence of correct decisions while concurrently gathering information about each possible decision. Solutions to the multi-armed bandit model have been used in applications for which evaluating all possible options is expensive or impossible, such as the optimal design of clinical trials~\cite{simon1989optimal}, market pricing~\cite{rothschild1974two}, and choosing strategies for games~\cite{st2012online}.

The traditional setting of a multi-armed bandit model is a gambler that has K independent slot machine arms and decides what machines to play, how many times to play each one, what order to play them in.
A successful gambler would want to exploit the machine that currently yields the highest reward and explore new arms to see if they give better rewards.
Developing a policy that successfully trades between exploration and exploitation has been the focus of extensive research since the problem formulation \cite{bubeck2009pure}, \cite{robbins1985some}, \cite{bergemann2006bandit}.

In our setting, we have a probabilistic  representation and would like to evaluate many potential grasps on the samples drawn from the graphical model in Fig. \ref{fig:graphical_model}.
Motivated by limited computational resources we are interested in how to intelligently allocate sampling resources to efficiently find the best grasp plan $\Gamma^*$.
Here each arm corresponds to a different grasp plan and pulling the arm is sampling from the graphical model in Fig. \ref{fig:graphical_model} and evaluating the arm's grasp plan on the sample.

A common measure of success in MAB problems is {\it regret}, the difference between the expected optimal reward and the expected reward of the selected arm on a single pull.
Traditional bandit algorithms minimize cumulative regret,  the sum of regret over the entire sequence of arm choices. Lai and Robbins showed that an optimal solution to the bandit problem is bounded by a logarithmic function \cite{lai1985asymptotically}. They presented an algorithm called (Upper Confidence Bound) UCB that obtains this bound asymptotically many variants of UCB have thus been purposed. The algorithm maintains a confidence bound on the distribution of reward based on prior observations and pulls the arm with the highest confidence bound.

In the case of grasping, one only cares about the regret when the grasp is actually executed. Hence, the exploration and exploitation stage are decoupled. Our goal is to identify the best arm in as few decisions as possible.
Given a set of arms $\lbrace 1,...K \rbrace$ with respective mean rewards $\mu_1, ..., \mu_K$ and the optimal arm $\mu^* = \underset{k\in\lbrace 1, ..., K \rbrace}{\mbox{max}} \mu_k$.
The simple regret at time $t$ is given by

@@

\section{Bandit Algorithms For Best Arm Identification}\label{sec:bandit_algorithm}

While, UCB type algorithms adopt a frequenist perspective for distributions with bounded rewards in their empirical estimate of an upper bound. A growing interest though in the MAB community is in bandit algorithms that have Bayesian approach \cite{kaufmann2012bayesian} \cite{agrawal2011analysis}. Here a prior distribution is placed on the distribution to be estimated and utilizing the prior enables a trade off between exploration and exploitation. Empirically Bayesian methods like Thompson sampling have been shown to outperform the UCB family \cite{chapelle2011empirical}.

In the context of grasping, the reward for pulling an arm is 1 if the grasp is in force closure on the sample and 0 if the grasp is not in force closure. This is a Bernoulli distribution which has a conjugate prior known as a Beta distribution. 
Hence, we can now model the distribution on rewards as a Beta-Bernoulli process. Bernoulli distributions are formally the probability $\theta$ that an event has occurred and a Beta distribution is the conjugate prior on the probability of theta or $p(\theta)$. Beta distributions are specified by shape parameters $\alpha$ and $\beta$, to update the prior Beta distribution one simply adds the count of observed successes of the event to $\alpha$ and the count of the observed failures to $\beta$. The default $\alpha =1 $ and $\beta =1$ corresponds to a uniform distribution on $\theta$.

Where $Q(\Gamma|\theta,\xi,\mu,z)$ is the grasp quality that is computed on a shape sample drawn from $p(\theta)$,$p(\xi)$,$p(\rho)$ and $p(\mu)$. Whats interesting in the context of a Bayesian BMAB problem our complicated graphical model in Fig. \ref{fig:graphical_model}, is now equivalent in terms of inference to \ref{fig:beta_model} and we only need to estimate $\alpha$ and $\beta$ to determine grasp quality. It is this intuition that helps explain the performance of the BMAB algorithms.

%In our case we only care about the regret at the time our decision of the optimal grasp needs to be made, decoupling the exploration and exploitation stages.

\subsection{Thompson Sampling}
Thompson Sampling is a Bayesian method for the multi-armed bandit problem. The main idea behind it is to update the conjugate prior for the distribution of the arm recently pulled, then sample from the prior distribution on all arms and pull the arm with the highest sample drawn. The full algorithm is shown in Algorithm 1.  Empirically this method has been shown to outperform frequentist methods like UCB in certain settings \cite{chapelle2011empirical}

@@

\subsection{Bayes-UCB}
Bayes UCB, detailed in Fig. 4, is a version of the UCB algorithm that uses a Bayesian posterior update to get a confidence bound instead of a the frequentist log(T ) term. To get an upper confidence bound from the posterior, the Bayes UCB algorithm uses the quantile of the Beta distribution up to a specified probability which depends on the timestep and horizon. Then the arm with the highest such quantile is chosen. For binary rewards the expected number of pulls of suboptimal arms is bounded and experimentally this algorithm has been shown to outperform UCB for binary rewards \cite{kaufmann2012bayesian}.

\begin{algorithm}
 \KwResult{Best Arm, $g^*$ }
 For Beta(1,1) prior, Stopping Horizon $n$: \\
\For{ t=1,2,...,n}{ 
	\For{j = 1,...,K}{

		Compute: $q_j(t) = Q\big(1-\frac{1}{t},p_j^{t-1}\big)$

	}
Draw arm$ I_t = \mbox{argmax}_{j=1...K}q_j(t)$\\
 Observe reward $X_{I_t,t} \in \lbrace 0,1 \rbrace$\\
 Update posterior:\\
 Set $S_{I_t,t+1} = S_{I_t,t} + X_{I_t,t}$ \\
 Set $F_{I_t,t+1} = F_{I_t,t} + 1 - X_{I_t,t}$\\
 Set $p_j^t \sim \mbox{Beta}(S_{I_t,t+1},F_{I_t,t+1} )$\\
 }
 \caption{Bayes-UCB for Beta-Bernoulli Process}
\end{algorithm}

\subsection{The Gittins Index Method} 
\todo{Let me know how clear this is, Gittins can be hard to describe in general}
One possible solution to solve the MAB problem is to treat it as an Markov Decision Process (MDP) and use Markov Decision theory. This solution makes a lot of sense when the distribution is known because the all elements in the standard MDP tuple, $\lbrace S,A,T,R,\gamma \rbrace$, would be known and it is optimal with respect $\gamma$.

@@

 .
\section{Experiments}
\subsection{Multi-Armed Bandit Experiments}
We consider the problem of selecting the best grasp plan, $\Gamma^*$ out of a set $G$. For our experiments we look at selecting the best grasp out of a size of $|G| = 1000$. In Fig. \ref{fig:simple_regret}, we plotted the simple regret averaged over 100 of the shapes in our data set and compare the different methods (UCB, Thompson, Gittins and the naive random allocation). We initialize both the Monte-Carlo and bandit technique by sampling each grasp 1 time. We draw samples from our calculated distributions $p(g)$.  Interestingly, Gittins and Thompson converge much faster than random and UCB. In Fig. \ref{fig:pulls_per_grasp}, you can see that Gittins and Thompson allocate grasp samples to only the grasps of high quality, thus it is quickly able to ignore the low quality grasps. UCB takes a more conservative approach to sample allocation, which leads to poor performance in the best arm identification problem \cite{bubeck2009pure}.

\begin{figure*}[ht!]
\centering
\includegraphics[width = 16.5cm, height = 9cm]{matlab_figures/simple_regret.eps}
\caption{ \footnotesize Comparison of Simple Regret convergence for the four sequential decision methods (Monte-Carlo, Bayes - UCB, Thompson, Gittins). Graph is averaged over 100 shapes from the Brown Sillohoute Dataset \cite{brown} with a set $|G|=1000$ for each shape. As you can see the BMAB methods converge almost a magnitude faster than random allocation. It is worth noting that Gittins outperform the other two algorithms, which is useful when choosing which one to implement }
\vspace*{-10pt}
\label{fig:simple_regret}
\end{figure*}

\begin{figure*}[ht!]
\centering
\includegraphics[width = 16.5cm, height = 9cm]{matlab_figures/pulls_per_grasp.eps}
\caption{ \footnotesize Comparison of sample per grasp for the four sequential decision methods (Random, Bayes - UCB, Thompson, Gittins). Graph is averaged over 100 shapes from the Brown Silhouette Dataset \cite{brown} with a set $|G|=1000$ for each shape. The best grasps are ranked 1 and worst are 1000. As you can see the MAB algorithm intelligently allocate samples towards high quality grasps based on past observations, where Monte-Carlo Integration takes a uniform approach to allocation. \cite{best_arm}}
\vspace*{-10pt}
\label{fig:pulls_per_grasp}
\end{figure*}
